Virtual Memory Assisted Transactional Memory for Dynamic Languages

### 2014-06-05 talk/dls2014/paper/paper.tex
bah, bogus micro benchmark

For the results in Figure~\ref{fig:scaling}, we averaged over 5 runs
and normalised the average runtimes to the time it took on a single
thread. From this we see that there is additional overhead introduced
by each thread (\remi{$13\%$} for all 4 threads together). While this
is not ideal, we think that \remi{$13\%$} are acceptable on four
threads. In terms of throughput, 4 threads have \remi{$3.53\times$}
more iterations per second than a single thread.

\remi{what we don't show is by how much this overhead is influenced
by allocations}

\cfbolz{why is the error so big with 4 threads?}

@@

We are still working on a number of optimizations in the
implementation.  We want to mention notably that memory usage has not
been optimized so far.  There are several sources of extra memory
requirements in our STM system.  The multiple nurseries add
4~MiB\footnote{Configurable value taken from experience with our
  non-STM reference interpreter.} per segment.  Additionally, the area
used for the read markers uses, per segment, up to 1/16th of the
memory used by the old objects.  With four segments, this adds $25\%$
to the total memory requirements.

@@

>>>>

For the results in Figure~\ref{fig:scaling}, we averaged over 5 runs
and normalised the average runtimes to the time it took on a single
thread. From this we see that there is additional overhead introduced
by each thread (\remi{$12.3\%$} for all 4 threads together). While this
is not ideal, we think that \remi{$12.3\%$} are acceptable on four
threads. In terms of throughput, 4 threads have \remi{$3.54\times$}
more iterations per second than a single thread.

@@

We are still working on a number of optimizations in the
implementation.  We want to mention notably that memory usage has not
been optimized so far.  There are several sources of extra memory
requirements in our STM system.  The multiple nurseries add
4~MiB\footnote{Configurable value taken from experience with our
  non-STM reference interpreter.} per segment.  Additionally, the area
used for the read markers uses, per segment, up to 1/16th of the
memory used by the old objects.  With four segments, this can add
as much as $25\%$ to the total memory requirements.

@@

Besides memory usage, we also want to mention scalability. We
think that current desktop machines with up to 8 cores should
be seen as the main area of applications of dynamic languages.
This is why our evaluation was performed on an off-the-shelf
desktop CPU with only 4 cores. In the future, we will look
at how far this STM system can really scale.
